% !TEX root = main.tex
\chapter{Concept Design}

  The following contains the conceptual design of a rear wing based on the previous chapters. First, a walkthrough of different airfoil profiles and their benefits is followed by selection of one particular. Secondly, analyzing the amount of elements the wing should consists of with regards to production time and ease of construction. A Product Design Specifiation (PDS) is set up to make sure that the design solution addresses all the problems it attempts to solve. Based on the PDS, an initial design is proposed, followed by a section describing the various possible methods of optimization.

  \section{Comparison of Airfoils}
    Choosing the MSHD wing.
    To be written from MSHD article on tuesday 19.

  \section{Multi elements? How many is enough}
    From katz book, written tuesday 19.

    Based on the previous section, a conceptual design of an aerodynamically

  \section{Product Design Specification (PDS)}

    \begin{tabularx}{\textwidth}[t]{l XX}
    \arrayrulecolor{seapurple}\hline
    \textbf{\textcolor{seapurple}{Issue}} & \textbf{\textcolor{seapurple}{Requirement}} & \textbf{\textcolor{seapurple}{Criteria}}\\
    \hline
    Weight & Must not move CM above halfway point & As low as possible  \\
    Safety & Must be in compliance with FSAE rules &   \\
    Durability & Must have no fatigue limit, has to be waterproof &   \\
    Performance & High downforce \& soft stall characteristic & Must retain perfomance despite tripping\\
    Dimensioning & Must be within area defined by FSAE rules & Easily mounted to current chassis\\
    Production & Low time and monetary cost &  \\
    \end{tabularx}
    %    \begin{minipage}[t]{\linewidth}%
    %      \begin{itemize}
    %        \item[1.1] Proportion of population below  purchasing power parity (PPP) a day
      %      \item[1.2] Poverty Gap ratio [incidence x depth of poverty]
      %      \item[1.3] Share of the poorest quintile in national consumption
      %    \end{itemize}
      %  \end{minipage}

  \section{Initial Design}

  \section{Optimization Tools}

    Also from katz book to be written tuesday 19.

    Building physical models is cool, wind tunnel time is expensive though

    Let's use CFD!

    To make sure CFD works, we need to perform experiments to verify simulations work.

    Let's make a small scale wind tunnel test and simulate the rest!
